Mega-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-10-30 analysis/Study1.qmd
added another sample
not completed (eyes hurt, sleep needed)

>>>>

### Sample 17

- Petzke et al 2024
- STAI - is the stai sf with 6 items (we use stait-trait)

df17 <- haven::read_sav("../data/Petzke2024/ETUDE1_main study.sav") |>
  select(id, age_to_be_completed_that_year, Gender, starts_with("IA0"), PHQ_15_total, DIF_total, DDF_total, EOT_total, PHQ_4_total, BPQ_total, STAI_total) |>
  rename(Age= age_to_be_completed_that_year,
         Heart = IA01_01, Hungry = IA01_02, Breathing = IA01_03, Thirsty = IA01_04, Urinate = IA01_05, 
         Defecate=IA01_06, Taste = IA01_07,Vomit = IA01_08, Sneeze = IA01_09, Cough = IA01_10, 
         Temp = IA01_11, Sex_arousal = IA01_12, Wind = IA01_13, Burp = IA01_14,Muscles = IA01_15, 
         Bruise = IA01_16, Pain = IA01_17, Blood_Sugar = IA01_18, Affective_touch = IA01_19, 
         Tickle =IA01_20, Itch = IA01_21,
         TAS_DIF = DIF_total, TAS_DDF =  DDF_total, TAS_EOT = EOT_total,
         PHQ15_Sum = PHQ_15_total,
         PHQ4_Sum = PHQ_4_total,
         BPQ_BodyAwareness = BPQ_total,
          ) |>
   mutate(Gender = case_when(
    Gender == 1 ~ "Male",
    Gender == 2 ~ "Female",
    Gender ==3 ~ "Other"))

#Ranges
df17$PHQ15_Sum <- df17$PHQ15_Sum/15
df17$BPQ_BodyAwareness <- df17$BPQ_BodyAwareness/12

df17$PHQ4_Depression <- (df13$PHQ4_Depression_4 + df13$PHQ4_Depression_3)/2
df13$PHQ4_Anxiety <- (df13$PHQ4_Anxiety_2 + df13$PHQ4_Anxiety_1)/2
